\section*{Detailed Tests}		

	\vspace{10pt}

	\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`_=8},frame=single,label=Test 1 output]
\textbf{[INFO]}	  	Connections Ready
\textbf{[Process: 2]}	[C]	Is now a Candidate.
\textbf{[Process: 1]}	[O]	Captured by Candidate Process: 2.
\textcolor{red}{\textbf{[Process: 2]}	[C]	Elected!}
\textbf{[Process: 1]}	[C]	Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 2]}	[C]	Level = 2.  Times Captured = 0.  Acks = 1.
\textbf{[INFO]}
\textbf{Level Sum - Number of Processes =} 1.	
\textbf{Captures Sum =} 1.	
\textbf{Total Kills =} 0 	
\textbf{Total Acks =} 1.
\textbf{Total number of Messages =} 2.
\textbf{Unsynchronized Captures =} 0.
	\end{Verbatim}

	\vspace{10pt}

	In this example , \textit{Test 1}, two processes are trying to get elected. Process 2 is the first candidate and captures Process 1 immediately, making itself the elected process. The '\textit{Level Sum - Number of Processes}' is equal to the '\textit{Captures Sum}', which proves the correctness of the algorithm for two processes.

	\vspace{10pt}
	
	\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`_=8},frame=single,label=Test 4 output]
\textbf{[INFO]}	  	Connections Ready
\textbf{[Process: 2]}	[C]	Is now a Candidate.
\textbf{[Process: 4]}	[C]	Is now a Candidate.
\textbf{[Process: 5]}	[C]	Is now a Candidate.
\textbf{[Process: 3]}	[C]	Is now a Candidate.
\textbf{[Process: 4]}	[O]	Captured by Candidate Process: 2.
\textbf{[Process: 6]}	[O]	Captured by Candidate Process: 4.
\textbf{[Process: 7]}	[O]	Captured by Candidate Process: 4.
\textbf{[Process: 8]}	[O]	Captured by Candidate Process: 4.
\textbf{[Process: 10}        [O]	Captured by Candidate Process: 5.
\textbf{[Process: 9]}	[O]	Captured by Candidate Process: 4.
\textbf{[Process: 2]}	[O]	Captured by Candidate Process: 5.
\textbf{[Process: 10]}       [O]	Captured by Candidate Process: 4.
\textbf{[Process: 5]}	[C]	Was Killed
\textbf{[Process: 6]}	[C]	Is now a Candidate.
\textbf{[Process: 5]}	[O]	Captured by Candidate Process: 4.
\textbf{[Process: 3]}	[O]	Captured by Candidate Process: 4.
\textbf{[Process: 2]}	[O]	Captured by Candidate Process: 4.
\textbf{[Process: 5]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 1]}	[O]	Captured by Candidate Process: 4.
\textbf{[Process: 5]}	[C]	Received a kill Message, but was already killed.
\textcolor{red}{\textbf{[Process: 4]}	[C]	Elected!} 
\textbf{[Process: 1]}	[C]	Level = 1.  Times Captured = 2.   Acks = 0.
\textbf{[Process: 2]}	[C]	Level = 2.  Times Captured = 2.   Acks = 1.
\textbf{[Process: 3]}	[C]	Level = 1.  Times Captured = 1.   Acks = 0.
\textbf{[Process: 4]}	[C]	Level = 10. Times Captured = 1.   Acks = 9.
\textbf{[Process: 5]}	[C]	Level = 4.  Times Captured = 1.   Acks = 6.
\textbf{[Process: 6]}	[C]	Level = 1.  Times Captured = 1.   Acks = 0.
\textbf{[Process: 7]}	[C]	Level = 1.  Times Captured = 1.   Acks = 0.
\textbf{[Process: 8]}	[C]	Level = 1.  Times Captured = 1.   Acks = 0.
\textbf{[Process: 9]}	[C]	Level = 1.  Times Captured = 1.   Acks = 0.
\textbf{[Process: 10]}       [C]	Level = 1.  Times Captured = 2.   Acks = 0.



\textbf{[INFO]}			
\textbf{Level Sum - Number of Processes =} 13.	
\textbf{Captures Sum =} 13.	
\textbf{Total Kills =} 3	
\textbf{Total Acks =} 16.
\textbf{Total number of Messages =} 33.
\textbf{Unsynchronized Captures =} 0.
	\end{Verbatim}

	\vspace{10pt}

	With this example from \textit{Test 4} we want to prove that even if more than on candidate starts the election at the same time, the algorithm still works as expected.

	\vspace{10pt}
	
	\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`_=8},frame=single,label=Test 6 output]
\textbf{[INFO]}	  	Connections Ready
\textbf{[Process: 35]}	[C]	Is now a Candidate.
\textbf{[Process: 25]}	[C]	Is now a Candidate.
\textbf{[Process: 7]}	 [O]	Captured by Candidate Process: 35.
\textbf{[Process: 17]}	[O]	Captured by Candidate Process: 25.
\textbf{[Process: 18]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 46]}	[O]	Captured by Candidate Process: 25.
\textbf{[Process: 47]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 49]}	[O]	Captured by Candidate Process: 25.
\textbf{[Process: 50]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 37]	}[O]	Captured by Candidate Process: 25.
\textbf{[Process: 42]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 35]}	[O]	Captured by Candidate Process: 25.
\textbf{[Process: 44]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 23]}	[O]	Captured by Candidate Process: 25.
\textbf{[Process: 11]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 36]}	[O]	Captured by Candidate Process: 25.
\textbf{[Process: 40]}	[O]	Captured by Candidate Process: 25.
\textbf{[Process: 49]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 25]}	[C]	Was Killed
\textbf{[Process: 41]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 12]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 19]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Is now a Candidate.
\textbf{[Process: 20]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 27]}	[O]	Captured by Candidate Process: 48.
\textbf{[Process: 31]}	[O]	Captured by Candidate Process: 48.
\textbf{[Process: 37]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 25]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 32]}	[O]	Captured by Candidate Process: 48.
\textbf{[Process: 33]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 16]}	[O]	Captured by Candidate Process: 48.
\textbf{[Process: 1]}	 [O]	Captured by Candidate Process: 35.
\textbf{[Process: 13]}	[O]	Captured by Candidate Process: 48.
\textbf{[Process: 37]}	[C]	Is now a Candidate.
\textbf{[Process: 10]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 26]}	[O]	Captured by Candidate Process: 48.
\textbf{[Process: 5]}	 [O]	Captured by Candidate Process: 48.
\textbf{[Process: 34]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 9]}	 [O]	Captured by Candidate Process: 48.
\textbf{[Process: 5]}	 [O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Was Killed
\textbf{[Process: 14]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 32]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 13]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 4]}	 [O]	Captured by Candidate Process: 35.
\textbf{[Process: 45]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 17]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 25]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 31]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 40]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 25]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 29]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 3]	} [O]	Captured by Candidate Process: 35.
\textbf{[Process: 38]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 26]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 48]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 2]}	 [O]	Captured by Candidate Process: 35.
\textbf{[Process: 15]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 6]}	 [O]	Captured by Candidate Process: 35.
\textbf{[Process: 8]}	 [O]	Captured by Candidate Process: 35.
\textbf{[Process: 28]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 28]}	[C]	Is now a Candidate.
\textbf{[Process: 27]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 25]	}[O]	Captured by Candidate Process: 35.
\textbf{[Process: 21]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 22]	}[O]	Captured by Candidate Process: 35.
\textbf{[Process: 46]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 25]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 39]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 16]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 36]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 25]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 9]	} [O]	Captured by Candidate Process: 35.
\textbf{[Process: 48]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 30]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 43]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 24]}	[O]	Captured by Candidate Process: 35.
\textbf{[Process: 19]}	[C]	Is now a Candidate.
\textbf{[Process: 25]}	[C]	Received a kill Message, but was already killed.
\textbf{[Process: 23]}	[O]	Captured by Candidate Process: 35.
\textcolor{red}{\textbf{[Process: 35]}	[C]	Elected!} 
\textbf{[Process: 1]}	 [C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 2]}	 [C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 3]}	 [C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 4]	} [C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 5]}	 [C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 6]}	 [C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 7]}	 [C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 8]}	 [C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 9]}	 [C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 10]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 11]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 12]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 13]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 14]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 15]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 16]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 17]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 18]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 19]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 20]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 21]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 22]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 23]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 24]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 25]}	[C]  Level = 9.  Times Captured = 1.  Acks = 14.
\textbf{[Process: 26]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 27]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 28]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 29]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 30]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 31]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 32]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 33]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 34]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 35]}	[C]  Level = 50.  Times Captured = 1. Acks = 49.
\textbf{[Process: 36]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 37]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 38]	}[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 39]	}[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 40]	}[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 41]	}[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 42]	}[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 43]	}[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 44]	}[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 45]	}[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 46]	}[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 47]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[Process: 48]}	[C]  Level = 9.  Times Captured = 1.  Acks = 16.
\textbf{[Process: 49]}	[C]  Level = 1.  Times Captured = 2.  Acks = 0.
\textbf{[Process: 50]}	[C]  Level = 1.  Times Captured = 1.  Acks = 0.
\textbf{[INFO]}		
\textbf{Level Sum - Number of Processes =} 65.	
\textbf{Captures Sum = }65.	
\textbf{Total Kills =} 15	
\textbf{Total Acks =} 79.
\textbf{Total number of Messages =} 163.
\textbf{Unsynchronized Captures =} 1.
	
	\end{Verbatim}

	\vspace{10pt}